### 2024-08-28 paper.tex
pass further

\section{The components of \(\mathcal{Q}\)}
\subsection{Setup}
Let \(X = J(\lambda) \in \gl_m\).
Let \((e_{ij})_{1 \leq i \leq k, 1 \leq j \leq \lambda_i}\) be the standard (Jordan) basis for \(\mathbb{C}^m\).
Let
\[\mathcal{Q} = \{(A_{0,b}, (V_i)) : \forall i. \; A_{0,b} V_{i + 1} \subseteq V_i\}.\]
In this section we find the irreducible components of \(\mathcal{Q}\).
\par We write \(b_{ij}\) to denote the projection of \(b \in \mathbb{C}^m\) onto \(e_{ij}\).
For each row \(i\), let \(p_i(b) = \max\{j : b_{ij} \neq 0\}\) (the maximum of the empty set is zero).
Then set \(q_i(b) = \lambda_i - p_i(b)\).
When it is clear enough from context where the \(b\) is coming from, we will just write \(p_i\) and \(q_i\) instead of \(p_i(b)\) and \(q_i(b)\).
\par Let \(I = \{i_1 < \cdots < i_r\} \subseteq \{1, ..., k\}\), and let \((\rho_i)_{i \in I}\) be any map \(I \to \mathbb{N}_{> 0}\) such that (1) \(\rho_i \leq \lambda_i\), (2) \(\rho_i\) is decreasing with \(i\), (3) \(\lambda_i - \rho_i\) is decreasing with \(i\), and (4) \(\rho_i < n\).
For notational convenience (although we assign meaning to neither \(i_0\) nor \(i_{r + 1}\)), we define \(q_{i_0} := n\), and \(p_{i_{r + 1}} := 0\).
Then, we define \(B_{I, (\rho_i)}\) as the set of \(b \in \mathbb{C}^m\) satisfying the following conditions.
\begin{itemize}
    \item For all \(k \in \{1, ..., r\}\), \(p_i = \rho_i\).
    \item For all \(k \in \{0, ..., r\}\), \(p_{i_{k + 1}} = \max_{i : q_i < q_{i_k}} p_i\).
\end{itemize}
Note that for any \(b \in B_{I, (\rho_i)}\) we have \(p_{i_1} > \cdots > p_{i_r} > p_{i_{r + 1}}\), and also \(q_{i_0} > q_{i_1} > \cdots > q_{i_r}\).
\par Let \(\mathcal{Q}_{I, (\rho_i)} := \{(A_{0, b}, (V_i)) \in \mathcal{Q} : b \in B_{I, (\rho_i)}\}\).
We will show that the \(\mathcal{Q}_{I, (\rho_i)}\)'s are the irreducible components of \(\mathcal{Q}\).

\begin{lemma}\label{bs_union}
    \(\mathbb{C}^m = \bigcup_{I, (\rho_i)} B_{I, (\rho_i)}\), where \(I\) ranges over all subsets of \(\{1, ..., k\}\), and \((\rho_i)\) ranges over all maps \(I \to \mathbb{N}_{>0}\) satisfying the conditions (1),(2),(3),(4).
    Further, none of the \(B_{I, (\rho_i)}\) is contained in the union of the others.
\end{lemma}
\begin{proof}
    Let \(b \in \mathbb{C}^m\).
    If \(\{i : q_{i_0} > q_i\}\) is the empty set, then stop.
    Otherwise, take any \(i_1 \in \argmax_{i : q_{i_0} > q_i} p_i\), and set \(\rho_{i_1} := p_{i_1}\).
    If \(\{i : q_{i_1} > q_i\} = \emptyset\), then stop.
    Otherwise, take any \(i_2 \in \argmax_{i : q_{i_1} > q_i} p_i\), and set \(\rho_{i_2} := p_{i_2}\).
    Continuing on in this way, eventually we reach a \(k\) where \(\{i : q_{i_k} > q_i\} = \emptyset\).
    Then we set \(I = \{i_1, ..., i_k\}\).
    Note that \(I, (\rho_i)\) satisfy conditions (1)--(4), and furthermore \(b \in B_{I, (\rho_i)}\).
    \par Now, we check that no \(B_{I, (\rho_i)}\) is contained in the union of the others.
    Fix \(I\) and \((\rho_i)\).
    Take any \(b \in B_{I, (\rho_i)}\) with \(p_i = \rho_i\) for \(i \in I\) and \(p_i = 0\) for \(i \notin I\).
    It is clear that \(b \notin B_{I', (\rho_i')}\) whenever \(I' \neq I\) or \((\rho_i') \neq (\rho_i)\).
\end{proof}

\subsection{Study of \(B_{I, (\rho_i)}\)}
Fix any \(I\) and \((\rho_i)\) satisfying the conditions (1)--(4).
As before, we write \(\{i_1 < \cdots < i_r\} := I\), and \(q_{i_0} := n\), and \(p_{i_{r + 1}} := 0\).

@@

\begin{corollary}\label{bs_iso}
    \[B_{I, (\rho_i)} \cong \prod_{k = 1}^r (\mathbb{C}^{\rho_{i_k} - 1} \times (\mathbb{C} \setminus \{0\})) \times \prod_{i : \lambda_i \geq q_{i_0} + p_{i_1}} \mathbb{C}^{\lambda_i - q_{i_0}} \times \prod_{k = 1}^r \prod_{\{i \notin I : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}}\mathbb{C}^{\min(p_{i_k}, \lambda_i - q_{i_k})}\]
\end{corollary}
\begin{proof}
    Here I use the notation \(x \times y = (x, y)\), and so on.
    The isomorphism sends \(b \in B_{I, (\rho_i)}\) to 
    \[\prod_{k = 1}^{r}(b_{i_k1},..., b_{i_k\rho_{i_k}}) \times \prod_{i : \lambda_i \geq q_{i_0} + p_{i_1}} (b_{i1}, ..., b_{i, \lambda_i - q_{i_0}}) \times\]
    \[\prod_{k = 1}^r \prod_{\{i \notin I : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}} (b_{i1}, ..., b_{i,\min(p_{i_k}, \lambda_i - q_{i_k})}).\]
    \cref{alternative_bs_two} tells us that this is an isomorphism.
\end{proof}

@@

\subsection{A study of \(U_{I, (\rho_i)}\)}
Fix any \(I\) and \((\rho_i)\) satisfying the conditions of Lemma 8.1.
We will find the irreducible components of \(U_{I, (\rho_i)}\), and show that their closures are in fact irreducible components of \(U_0\).
\par I claim that \(A_{0,b}\) has the same shape for every \((A_{0, b}, U) \in U_{I, (\rho_i)}\).
Call this shape \(\mu\).
By finding a algebraic map taking \(b\) to a Jordan basis for \(A_{0,b}\), we will put \(U_{I, (\rho_i)}\) in isomorphism with the product (choice of \(b\)) \(\times\) (Springer fiber at \(J(\mu)\)).
Then we will use our result about the usual Springer fiber at \(J(\mu)\) to find the irreducible components of \(U_{I, (\rho_i)}\).

@@

@@

        First we note that \(q_{i_k} < n\) by the definition of \(U_{I, (\rho_i)}\), so the definition of \(v_{i_k}\) makes sense.

@@

        \[\sum_{i \notin I} (p_i + q_i) + (n + P) + \sum_{i \in I} (q_i + P_i).\]
        Writing \(I = \{i_1 < \cdots < i_{|I|}\}\), we note that \(P = p_{i_1}\), that \(P_{i_{|I|}} = 0\), and that for \(l < |I|\) we have \(P_{i_l} = p_{i_{l + 1}}\).
        Thus, the sum above is 
        \[\sum_{i \notin I} (p_i + q_i) + (n + p_{i_1}) + \sum_{l = 1}^{|I|} (q_{i_l} + p_{i_{l + 1}}) = \]
        \[\sum_{i \notin I} (p_i + q_i) + n + \sum_{l = 1}^{|I|} (q_{i_l} + p_{i_l}) = n + \sum_i (q_i + p_i) = m + n.\]

@@

        To see this, we consider the chain beginning with \(f_n - (A^{n + P} f_n \rightshift n + P)\).
        As explained in the proof of (1), we have \(A^{n + P} f_n \in \langle e_{ij}\rangle_{i,j : q_i \geq n}\).
        Consequently, \((A^{n + P} f_n \rightshift n + P) \in \langle e_{ij} \rangle_{i,j : q_i \geq n} \subseteq W\).
        Because \(f_n - (A^{n + P} f_n \rightshift n + P) \in W\), this implies that \(f_n \in W\).
        \par Because \(AW \subseteq W\) (obvious, since \(W\) is the span of chains), the fact that \(f_n \in W\) implies that \(f_i \in W\) for each \(i\), and also \(b \leftshift l \in W\) for each \(l \geq 0\).
        \par Now we are left with showing that \(\langle e_{ij} \rangle_{i,j : q_i < n} \subseteq W\).

@@

@@

\begin{lemma}\label{u_i_rho_iso}
    \(U_{I, (\rho_i)} \cong B_{I, (\rho_i)} \times X_\mu\).
\end{lemma}
\begin{proof}
    For \(b \in B_{I, (\rho_i)}\), let \(P_b\) be the change-of-basis matrix, with columns given by the Jordan basis of the previous lemma, so that \(J(\mu) = P_b^{-1} A_{0,b} P_b\).
    From looking at the Jordan basis of the previous lemma (the basis can be expressed in terms of \(A, \lambda, e_{ij}, f_i, I, \rho_i, b\)), it is clear that the map \(P : B_{I, (\rho_i)} \to \GL_{m + n}\), given by \(b \mapsto P_b\), is algebraic.
    \par Now, we remark that the Springer fiber at \(A_{0,b}\) is simply \(\{P_b U : U \in X_\mu\}\).
    This gives us the isomorphism \(B_{I, (\rho_i)} \times X_\mu \to U_{I, (\rho_i)}\).
    \[(b, U) \mapsto (P_b J(\mu) P_b^{-1}, P_b U),\]
    with inverse
    \[(A_{0,b}, U) \mapsto (b, P_b^{-1} U).\]
\end{proof}

\begin{corollary}\label{u_i_rho_irred_and_dim}
    The 
    \(U_{I, (\rho_i)}\) is irreducible, and its dimension is \(\gamma([0, \lambda_1, ..., \lambda_k])\).
\end{corollary}
\begin{proof}
    Irreducibility follows from \cref{u_i_rho_iso}, since \(B_{I, (\rho_i)}\) is irreducible (by \cref{bs_iso}), as is \(X_\mu\).
    To get the dimension, we add the dimension of \(B_{I, (\rho_i)}\) to the dimension of \(X_\mu\).
    The dimension of \(X_\mu\) is 
\end{proof}

\subsection{Conclusion}
At last we have reached the base of our recursive procedure, and we begin to propagate upwards.
We write \((X_{\mu, \alpha})_\alpha\) to denote the irreducible components of \(X_\mu\).
\begin{lemma}
    The irreducible components of \(U_{I, (\rho_i)}\) are exactly the subvarieties 
    \[U_{I, (\rho_i), \alpha} := \{(P_b J(\mu) P_b^{-1}, P_b U) : b \in B_{I, (\rho_i)}, U \in X_{\mu, \alpha}\}.\]
    These are distinct.  
    There are blah of them, and each has dimension blah.
\end{lemma}
\begin{proof}
    We know from \cref{bs_iso} that \(B_{I, (\rho_i)}\) is irreducible.
    So, the components of \(B_{I, (\rho_i)} \times X_\mu\) are obviously \(B_{I, (\rho_i)} \times X_{\mu, \alpha}\).
    Their dimensions are blah, and there are... of them.
    taking image under the isomorphism gives the desired result.
\end{proof}

>>>>

\section{The components of \(\mathcal{Q}\)}
\subsection{Setup}
Let \(X = J(\lambda) \in \gl_m\).
Let \((e_{ij})_{1 \leq i \leq k, 1 \leq j \leq \lambda_i}\) be the standard (Jordan) basis for \(\mathbb{C}^m\).
Let
\[\mathcal{Q} = \{(A_{0,b}, (V_i)) : \forall i. \; A_{0,b} V_{i + 1} \subseteq V_i\}.\]
In this section we find the irreducible components of \(\mathcal{Q}\).
\par We write \(b_{ij}\) to denote the projection of \(b \in \mathbb{C}^m\) onto \(e_{ij}\).
For each row \(i\), let \(p_i(b) = \max\{j : b_{ij} \neq 0\}\) (the maximum of the empty set is zero).
Then set \(q_i(b) = \lambda_i - p_i(b)\).
When it is clear enough from context where the \(b\) is coming from, we will just write \(p_i\) and \(q_i\) instead of \(p_i(b)\) and \(q_i(b)\).
\par Let \(I = \{i_1 < \cdots < i_r\} \subseteq \{1, ..., k\}\), and let \((\rho_i)_{i \in I}\) be any map \(I \to \mathbb{N}_{> 0}\) such that (1) \(\rho_i \leq \lambda_i\), (2) \(\rho_i\) is decreasing with \(i\), (3) \(\lambda_i - \rho_i\) is decreasing with \(i\), and (4) \(\rho_i < n\).
For notational convenience (although we assign meaning to neither \(i_0\) nor \(i_{r + 1}\)), we define \(q_{i_0} := n\), and \(p_{i_{r + 1}} := 0\).
Then, we define \(B_{I, (\rho_i)}\) as the set of \(b \in \mathbb{C}^m\) satisfying the following conditions.
\begin{itemize}
    \item For all \(k \in \{1, ..., r\}\), \(p_i = \rho_i\).
    \item For all \(k \in \{0, ..., r\}\), \(p_{i_{k + 1}} = \max_{i : q_i < q_{i_k}} p_i\).
\end{itemize}
Note that for any \(b \in B_{I, (\rho_i)}\) we have \(p_{i_1} > \cdots > p_{i_r} > p_{i_{r + 1}}\), and also \(q_{i_0} > q_{i_1} > \cdots > q_{i_r}\).

\begin{lemma}\label{bs_union}
    \(\mathbb{C}^m = \bigcup_{I, (\rho_i)} B_{I, (\rho_i)}\), where \(I\) ranges over all subsets of \(\{1, ..., k\}\), and \((\rho_i)\) ranges over all maps \(I \to \mathbb{N}_{>0}\) satisfying the conditions (1),(2),(3),(4).
    Further, none of the \(B_{I, (\rho_i)}\) is contained in the union of the others.
\end{lemma}
\begin{proof}
    Let \(b \in \mathbb{C}^m\).
    If \(\{i : q_{i_0} > q_i\}\) is the empty set, then stop.
    Otherwise, take any \(i_1 \in \argmax_{i : q_{i_0} > q_i} p_i\), and set \(\rho_{i_1} := p_{i_1}\).
    If \(\{i : q_{i_1} > q_i\} = \emptyset\), then stop.
    Otherwise, take any \(i_2 \in \argmax_{i : q_{i_1} > q_i} p_i\), and set \(\rho_{i_2} := p_{i_2}\).
    Continuing on in this way, eventually we reach a \(k\) where \(\{i : q_{i_k} > q_i\} = \emptyset\).
    Then we set \(I = \{i_1, ..., i_k\}\).
    Note that \(I, (\rho_i)\) satisfy conditions (1)--(4), and furthermore \(b \in B_{I, (\rho_i)}\).
    \par Now, we check that no \(B_{I, (\rho_i)}\) is contained in the union of the others.
    Fix \(I\) and \((\rho_i)\).
    Take any \(b \in B_{I, (\rho_i)}\) with \(p_i = \rho_i\) for \(i \in I\) and \(p_i = 0\) for \(i \notin I\).
    It is clear that \(b \notin B_{I', (\rho_i')}\) whenever \(I' \neq I\) or \((\rho_i') \neq (\rho_i)\).
\end{proof}
\par Let \(\mathcal{Q}_{I, (\rho_i)} := \{(A_{0, b}, (V_i)) \in \mathcal{Q} : b \in B_{I, (\rho_i)}\}\).
We will show that \(\mathcal{Q}_{I, (\rho_i)} \cong B_{I, (\rho_i)} \times (\textrm{some springer fiber})\).
Then we will use the result about the irreducible components of a Springer fiber to find the irreducible components of \(\mathcal{Q}_{I, (\rho_i)}\), and the closures of these will be the irreducible components of \(\mathcal{Q}\).

\subsection{Study of \(B_{I, (\rho_i)}\)}
Fix any \(I\) and \((\rho_i)\) satisfying the conditions (1)--(4) of \cref{bs_union}.
As before, we write \(\{i_1 < \cdots < i_r\} := I\), and \(q_{i_0} := n\), and \(p_{i_{r + 1}} := 0\).

@@

\begin{corollary}\label{bs_iso}
    \begin{align*}
        B_{I, (\rho_i)} \cong & \prod_{k = 1}^r (\mathbb{C}^{\rho_{i_k} - 1} \times (\mathbb{C} \setminus \{0\})) \times \prod_{i : \lambda_i \geq q_{i_0} + p_{i_1}} \mathbb{C}^{\lambda_i - q_{i_0}} \times \\
        & \prod_{k = 1}^r \prod_{\{i \notin I : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}}\mathbb{C}^{\min(p_{i_k}, \lambda_i - q_{i_k})}.
    \end{align*}
\end{corollary}
\begin{proof}
    Here I use the notation \(x \times y = (x, y)\), and so on.
    The isomorphism sends \(b \in B_{I, (\rho_i)}\) to 
    \[\prod_{k = 1}^{r}(b_{i_k1},..., b_{i_k\rho_{i_k}}) \times \prod_{i : \lambda_i \geq q_{i_0} + p_{i_1}} (b_{i1}, ..., b_{i, \lambda_i - q_{i_0}}) \times\]
    \[\prod_{k = 1}^r \prod_{\{i \notin I : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}} (b_{i1}, ..., b_{i,\min(p_{i_k}, \lambda_i - q_{i_k})}).\]
    \cref{alternative_bs_two} says that this is an isomorphism.
\end{proof}

@@

\subsection{Study of \(\mathcal{Q}_{I, (\rho_i)}\)}
Fix any \(I\) and \((\rho_i)\) satisfying the conditions (1)--(4) of \cref{bs_union}.
In this subsection we find the irreducible components of \(\mathcal{Q}_{I, (\rho_i)}\).
\par I claim that there is some \(\mu(I, (\rho_i))\) such that every \((A_{0, b}, U) \in \mathcal{Q}_{I, (\rho_i)}\) is similar to \(J(\mu)\).
By finding a algebraic map taking \(b \in B_{I, (\rho_i)}\) to a Jordan basis for \(A_{0,b}\), we will put \(\mathcal{Q}_{I, (\rho_i)}\) in isomorphism with the product \(B_{I, (\rho_i)} \times (Springer fiber at J(\mu))\).
Then we will use our result about the usual Springer fiber at \(J(\mu)\) to find the irreducible components of \(\mathcal{Q}_{I, (\rho_i)}\).

@@

As before, we write \(\{i_1, ..., i_r\} := I\), and \(q_{i_0} := n\), and \(p_{i_{r + 1}} := 0\).
We also write, somewhat abusively, \(b \in \mathbb{C}^{m + n}\) to refer to the vector \((b, 0) \in \mathbb{C}^{m + n}\).

@@

        First we note that \(q_{i_k} < n\) by the definition of \(\mathcal{Q}_{I, (\rho_i)}\), so the definition of \(v_{i_k}\) makes sense.

@@

        \[\sum_{i \notin I} (p_i + q_i) + \sum_{k = 0}^r (q_{i_k} + p_{i_{k + 1}}) = \sum_i (q_i + p_i) = m + n.\]

@@

        To see this, we consider the chain beginning with \(f_n - (A^{n + p_{i_1}} f_n \rightshift n + p_{i_1})\).
        As explained in the proof of (1), we have \(A^{n + p_{i_1}} f_n \in \langle e_{ij}\rangle_{i,j : q_i \geq n}\).
        Consequently, \((A^{n + p_{i_1}} f_n \rightshift n + p_{i_1}) \in \langle e_{ij} \rangle_{i,j : q_i \geq n} \subseteq W\).
        Because \(f_n - (A^{n + p_{i_1}} f_n \rightshift n + p_{i_1}) \in W\), this implies that \(f_n \in W\).
        \par Because \(AW \subseteq W\) (obvious, since \(W\) is a span of chains), the fact that \(f_n \in W\) implies that \(f_i \in W\) for each \(i\), and also \(b \leftshift l \in W\) for each \(l \geq 0\).
        \par CONTINUE HERE.
        Now we are left with showing that \(\langle e_{ij} \rangle_{i,j : q_i < n} \subseteq W\).

@@

        So, we just need to show that \(e_{i_kj}\)

@@

\begin{lemma}\label{u_i_rho_iso}
    \(\mathcal{Q}_{I, (\rho_i)} \cong B_{I, (\rho_i)} \times X_\mu\).
\end{lemma}
\begin{proof}
    For \(b \in B_{I, (\rho_i)}\), let \(P_b\) be the change-of-basis matrix, with columns given by the Jordan basis of the previous lemma, so that \(J(\mu) = P_b^{-1} A_{0,b} P_b\).
    From looking at the Jordan basis of the previous lemma (the basis can be expressed in terms of \(A, \lambda, e_{ij}, f_i, I, \rho_i, b\)), it is clear that the map \(P : B_{I, (\rho_i)} \to \GL_{m + n}\), given by \(b \mapsto P_b\), is algebraic.
    \par Now, we remark that the Springer fiber at \(A_{0,b}\) is simply \(\{P_b U : U \in X_\mu\}\).
    This gives us the isomorphism \(B_{I, (\rho_i)} \times X_\mu \to \mathcal{Q}_{I, (\rho_i)}\).
    \[(b, U) \mapsto (P_b J(\mu) P_b^{-1}, P_b U),\]
    with inverse
    \[(A_{0,b}, U) \mapsto (b, P_b^{-1} U).\]
\end{proof}

\begin{corollary}\label{u_i_rho_irred_and_dim}
    The 
    \(\mathcal{Q}_{I, (\rho_i)}\) is irreducible, and its dimension is \(\gamma([0, \lambda_1, ..., \lambda_k])\).
\end{corollary}
\begin{proof}
    Irreducibility follows from \cref{u_i_rho_iso}, since \(B_{I, (\rho_i)}\) is irreducible (by \cref{bs_iso}), as is \(X_\mu\).
    To get the dimension, we add the dimension of \(B_{I, (\rho_i)}\) to the dimension of \(X_\mu\).
    The dimension of \(X_\mu\) is 
\end{proof}

\subsection{Conclusion}
At last we have reached the base of our recursive procedure, and we begin to propagate upwards.
We write \((X_{\mu, \alpha})_\alpha\) to denote the irreducible components of \(X_\mu\).
\begin{lemma}
    The irreducible components of \(\mathcal{Q}_{I, (\rho_i)}\) are exactly the subvarieties 
    \[U_{I, (\rho_i), \alpha} := \{(P_b J(\mu) P_b^{-1}, P_b U) : b \in B_{I, (\rho_i)}, U \in X_{\mu, \alpha}\}.\]
    These are distinct.  
    There are blah of them, and each has dimension blah.
\end{lemma}
\begin{proof}
    We know from \cref{bs_iso} that \(B_{I, (\rho_i)}\) is irreducible.
    So, the components of \(B_{I, (\rho_i)} \times X_\mu\) are obviously \(B_{I, (\rho_i)} \times X_{\mu, \alpha}\).
    Their dimensions are blah, and there are... of them.
    taking image under the isomorphism gives the desired result.
\end{proof}
